TBD

### 2016-10-07 paper.tex
interesting observation

Replacing $\breve{\br}$ with $\breve{\bd}-\breve{\bv}$ in Eq.~\eqref{eq:GN_update} results in
\begin{equation}
\label{eq:temp_GN_eq}
\Delta \breve{\bz} = (\bJ^H\bJ)^{-1}\bJ^H(\breve{\bd}-\breve{\bv}), 
\end{equation}
Substituting the first identity of Eq.~\eqref{eq:identities} into Eq.~\eqref{eq:temp_GN_eq} and simplifying we obtain
\begin{equation}
\label{eq:two_thrids}
\Delta \breve{\bz} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\bd}-\frac{1}{3}\breve{\bz}.
\end{equation}
It now trivially follows from Eq.~\eqref{eq:two_thrids} that:
\begin{equation}
\breve{\bz}_{k+1} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\bd} + \frac{2}{3}\breve{\bz}_{k}. 
\end{equation}
%STILL NEED TO ADD z k+1 EXPRESSION.
THE TAKE HOME HERE IS WE CAN CALCULATE THE UPDATE STEP WITHOUT CALCULATING THE RESIDUAL.

@@

Inspecting Eq.~\eqref{eq:red_H} reveals that in the case of redundant calibration the Hessian's diagonal entries are also more significant than its off-diagonal entries.
If we substitute $\bJ^H\bJ$ with $\widetilde{\bH}$ (by its diagonal approximation) and replace $\breve{\br}$ with $\breve{\bd} - \breve{\bv}$ in Eq.~\eqref{eq:GN_update} we obtain
\begin{equation}
\label{eq:appr_GN}
 \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H(\breve{\bd}-\breve{\bv})
\end{equation}
Utilizing the second identity in Eq.~\eqref{eq:identities} allows us to simplify Eq.~\eqref{eq:appr_GN} to
\begin{equation}
  \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}-\breve{\bz}.
\end{equation}
It now trivially follows that
\begin{equation}
 \breve{\bz}_{k+1} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}.
\end{equation}
We obtain a similar result if we repeat the above procedure, only in this case we use Eq.~\eqref{eq:LM_update} instead,
namely
\begin{align}
\breve{\bz}_{k+1} &\approx \frac{1}{1+\lambda}\widetilde{\bH}^{-1}\bJ^H\breve{\bd} + \frac{\lambda}{1+\lambda} \breve{\bz}_k,\label{eq:lambda}\\
 &= \alpha \widetilde{\bH}^{-1}\bJ^H\breve{\bd} + (1-\alpha)\breve{\bz}_k, \label{eq:alpha}  
\end{align}
where $\alpha = \frac{1}{1+\lambda}$. Moreover, $\lambda = \frac{1-\alpha}{\alpha}$. The analytic expression of $\bJ^H\breve{\bd}$ will be very similar to the analytic 
expression of $\bJ^H\breve{\br}$, the only difference being that in Eq.~\eqref{eq:ab} the letter $r$ would be replaced by a $d$. If we substitute the analytic expression
of $\bJ^H\breve{\bd}$ and $\widetilde{\bH}^{-1}$ (which is easily computed as the matrix is a diagonal matrix) into Eq.~\eqref{eq:alpha} we obtain the following two update rules:
\begin{equation}
\label{eq:g_update}
g_{i}^{k+1} = \alpha \frac{\sum_{j\neq i} g_j^k \widetilde{y}_{ij}^{~\!\!k} d_{ij}}{\sum_{j\neq i} |g_j^k|^2|y_{\zeta_{ij}}^k|^2} + (1-\alpha) g_i^k, 
\end{equation}
and
\begin{equation}
\label{eq:y_update}
y_{i}^{k+1} = \alpha \frac{\sum_{pq \in \mathcal{PQ}_i} \conj{g}_p^k g_q^k d_{pq}}{\sum_{pq \in \mathcal{PQ}_i}|g_p^k|^2|g_q^k|^2} + (1-\alpha) y_i^k 
\end{equation}

>>>>

Replacing $\breve{\br}$ with $\breve{\bd}-\breve{\bv}$ in Eq.~\eqref{eq:GN_update} results in
\begin{equation}
\label{eq:temp_GN_eq}
\Delta \breve{\bz} = (\bJ^H\bJ)^{-1}\bJ^H(\breve{\bd}-\breve{\bv}), 
\end{equation}
Substituting the first identity of Eq.~\eqref{eq:identities} into Eq.~\eqref{eq:temp_GN_eq} and simplifying we obtain
\begin{equation}
\label{eq:one_thrid}
\Delta \breve{\bz} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\bd}-\frac{1}{3}\breve{\bz}.
\end{equation}
It now trivially follows from Eq.~\eqref{eq:one_thrid} that:
\begin{equation}
\label{eq:two_thrids}
\breve{\bz}_{k+1} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\bd} + \frac{2}{3}\breve{\bz}_{k}. 
\end{equation}
%STILL NEED TO ADD z k+1 EXPRESSION.
THE TAKE HOME HERE IS WE CAN CALCULATE THE UPDATE STEP WITHOUT CALCULATING THE RESIDUAL.

@@

Inspecting Eq.~\eqref{eq:red_H} reveals that in the case of redundant calibration the Hessian's diagonal entries are also more significant than its off-diagonal entries.
If we substitute $\bJ^H\bJ$ with $\widetilde{\bH}$ (by its diagonal approximation) and replace $\breve{\br}$ with $\breve{\bd} - \breve{\bv}$ in Eq.~\eqref{eq:GN_update} we obtain
\begin{equation}
\label{eq:appr_GN}
 \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H(\breve{\bd}-\breve{\bv})
\end{equation}
Utilizing the second identity in Eq.~\eqref{eq:identities} allows us to simplify Eq.~\eqref{eq:appr_GN} to
\begin{equation}
  \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}-\breve{\bz}.
\end{equation}
It now trivially follows that
\begin{equation}
 \breve{\bz}_{k+1} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}.
\end{equation}
We obtain a similar result if we repeat the above procedure, only in this case we use Eq.~\eqref{eq:LM_update} instead,
namely
\begin{align}
\breve{\bz}_{k+1} &\approx \frac{1}{1+\lambda}\widetilde{\bH}^{-1}\bJ^H\breve{\bd} + \frac{\lambda}{1+\lambda} \breve{\bz}_k,\label{eq:lambda}\\
 &= \alpha \widetilde{\bH}^{-1}\bJ^H\breve{\bd} + (1-\alpha)\breve{\bz}_k, \label{eq:alpha}  
\end{align}
where $\alpha = \frac{1}{1+\lambda}$. Moreover, $\lambda = \frac{1-\alpha}{\alpha}$. The analytic expression of $\bJ^H\breve{\bd}$ will be very similar to the analytic 
expression of $\bJ^H\breve{\br}$, the only difference being that in Eq.~\eqref{eq:ab} the letter $r$ would be replaced by a $d$. If we substitute the analytic expression
of $\bJ^H\breve{\bd}$ and $\widetilde{\bH}^{-1}$ (which is easily computed as the matrix is a diagonal matrix) into Eq.~\eqref{eq:alpha} we obtain the following two update rules:
\begin{equation}
\label{eq:g_update}
g_{i}^{k+1} = \alpha \frac{\sum_{j\neq i} g_j^k \widetilde{y}_{ij}^{~\!\!k} d_{ij}}{\sum_{j\neq i} |g_j^k|^2|y_{\zeta_{ij}}^k|^2} + (1-\alpha) g_i^k, 
\end{equation}
and
\begin{equation}
\label{eq:y_update}
y_{i}^{k+1} = \alpha \frac{\sum_{pq \in \mathcal{PQ}_i} \conj{g}_p^k g_q^k d_{pq}}{\sum_{pq \in \mathcal{PQ}_i}|g_p^k|^2|g_q^k|^2} + (1-\alpha) y_i^k. 
\end{equation}

The question now arises what value should we use for $\alpha$? Although an exact mathematical proof for the optimal choice of $\alpha$ still eludes us, it is still possible to
venture a clever guess by studying what the choice of $\alpha$ is in the case of StEFCal. The StEFCal equivalent of Eq.~\eqref{eq:two_thrids}
is equal to
\begin{equation}
\label{eq:one_half}
\breve{\bg}_{k+1} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\bd} + \frac{1}{2}\breve{\bg}_{k}. 
\end{equation}
Note that in Eq.~\eqref{eq:one_half} the influence that the estimate of the parameters from the previous iteration has on the current iteration is scaled by a half, while
in Eq.~\eqref{eq:two_thrids} it is scaled by two thirds. Moreover, the StEFCal equivalent of Eq.~\eqref{eq:lambda} and Eq.~\eqref{eq:alpha} are
\begin{align}
\breve{\bg}_{k+1} &\approx \frac{1}{1+\lambda}\widetilde{\bH}^{-1}\bJ^H\breve{\bd} + \frac{\lambda}{1+\lambda} \breve{\bg}_k,\label{eq:stef_lambda}\\
 &= \alpha \widetilde{\bH}^{-1}\bJ^H\breve{\bd} + (1-\alpha)\breve{\bg}_k, \label{eq:stef_alpha}  
\end{align}

On the odd iterations $\lambda$ is chosen to be zero, which corresponds to an $\alpha$ equal to one. On the even iteration $\lambda$ is chosen to be equal to one, which corresponds
to an $\alpha$ equal to a half. On the odd iteration

\begin{align}
\breve{\bz}_{k+1} &\approx \frac{1}{1+\lambda}\widetilde{\bH}^{-1}\bJ^H\breve{\bd} + \frac{\lambda}{1+\lambda} \breve{\bz}_k,\label{eq:lambda}\\
 &= \alpha \widetilde{\bH}^{-1}\bJ^H\breve{\bd} + (1-\alpha)\breve{\bz}_k, \label{eq:alpha}  
\end{align}
